\bf The Right Arm Bias in ITF Taekwon-Do \\ Patterns Chon-Ji to Juche

### 2012-02-24 article.tex
Reduced size on figures

  % Distribution of techniques by category
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/techniques_all}
    \caption{Distribution of techniques by category.}
    \label{fig:techniques_all}
  \end{figure}

@@

  % all techniques by height
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/height_all}
    \caption{All techniques by height.}
    \label{fig:height_all}
  \end{figure}

@@

  % All techniques by Walking, Sitting and L stances
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_all}
    \caption{All techniques by walking, sitting and L stances.}
    \label{fig:stances_all}
  \end{figure}

@@

  % All techniques by stances except walking, sitting and L stances
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_not_wsl}
    \caption{All techniques by stances except walking, sitting and L stances.}
    \label{fig:stances_not_wsl}
  \end{figure}

@@

  % Left techniques by stances except walking, sitting and L
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_left_not_wsl}
    \caption{Left techniques by stances except walking, sitting and L stances.}
    \label{fig:stances_left_not_wsl}
  \end{figure}

  % Right techniques by stances except walking, sitting and L
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_right_not_wsl}
    \caption{Right techniques by stances except walking, sitting and L
    stances.}
    \label{fig:stances_right_not_wsl}
  \end{figure}

@@

  % all techniques by motion type
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_all}
    \caption{All techniques by all motion types.}
    \label{fig:motion_all}
  \end{figure}

@@

  % all techniques by motion type except normal motion
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_all_not_n}
    \caption{All techniques by motion type except normal motion.}
    \label{fig:motion_all_not_n}
  \end{figure}

@@

  % left techniques by motion type except normal motion
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_left_not_n}
    \caption{Left techniques by motion type except normal motion.}
    \label{fig:motion_left_not_n}
  \end{figure}

  % right techniques by motion type except normal motion
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_right_not_n}
    \caption{Right techniques by motion type except normal motion.}
    \label{fig:motion_right_not_n}
  \end{figure}

@@

  % all techniques by patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_all}
    \caption{All techniques by patterns.}
    \label{fig:patterns_all}
  \end{figure}

  % all techniques by black belt patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_all}
    \caption{All techniques by black belt patterns.}
    \label{fig:patterns_black_all}
  \end{figure}

  % all techniques by color belt patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_all}
    \caption{All techniques by color belt patterns.}
    \label{fig:patterns_color_all}
  \end{figure}

@@

  % left techniques by patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_left}
    \caption{Left techniques by patterns.}
    \label{fig:patterns_left}
  \end{figure}

  % right techniques by patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_right}
    \caption{Right techniques by patterns.}
    \label{fig:patterns_right}
  \end{figure}

>>>>

  % Distribution of techniques by category
  \begin{figure}
    \includegraphics[scale=0.65]{data/gnuplot/eps/techniques_all}
    \caption{Distribution of techniques by category.}
    \label{fig:techniques_all}
  \end{figure}

@@

  % all techniques by height
  \begin{figure}
    \includegraphics[scale=0.65]{data/gnuplot/eps/height_all}
    \caption{All techniques by height.}
    \label{fig:height_all}
  \end{figure}

@@

  % All techniques by Walking, Sitting and L stances
  \begin{figure}
    \includegraphics[scale=0.65]{data/gnuplot/eps/stances_all}
    \caption{All techniques by walking, sitting and L stances.}
    \label{fig:stances_all}
  \end{figure}

@@

  % All techniques by stances except walking, sitting and L stances
  \begin{figure}
    \includegraphics[scale=0.65]{data/gnuplot/eps/stances_not_wsl}
    \caption{All techniques by stances except walking, sitting and L stances.}
    \label{fig:stances_not_wsl}
  \end{figure}

@@

  % Left techniques by stances except walking, sitting and L
  \begin{figure}
    \includegraphics[scale=0.65]{data/gnuplot/eps/stances_left_not_wsl}
    \caption{Left techniques by stances except walking, sitting and L stances.}
    \label{fig:stances_left_not_wsl}
  \end{figure}

  % Right techniques by stances except walking, sitting and L
  \begin{figure}
    \includegraphics[scale=0.65]{data/gnuplot/eps/stances_right_not_wsl}
    \caption{Right techniques by stances except walking, sitting and L
    stances.}
    \label{fig:stances_right_not_wsl}
  \end{figure}

@@

  % all techniques by motion type
  \begin{figure}
    \includegraphics[scale=0.65]{data/gnuplot/eps/motion_all}
    \caption{All techniques by all motion types.}
    \label{fig:motion_all}
  \end{figure}

@@

  % all techniques by motion type except normal motion
  \begin{figure}
    \includegraphics[scale=0.65]{data/gnuplot/eps/motion_all_not_n}
    \caption{All techniques by motion type except normal motion.}
    \label{fig:motion_all_not_n}
  \end{figure}

@@

  % left techniques by motion type except normal motion
  \begin{figure}
    \includegraphics[scale=0.65]{data/gnuplot/eps/motion_left_not_n}
    \caption{Left techniques by motion type except normal motion.}
    \label{fig:motion_left_not_n}
  \end{figure}

  % right techniques by motion type except normal motion
  \begin{figure}
    \includegraphics[scale=0.65]{data/gnuplot/eps/motion_right_not_n}
    \caption{Right techniques by motion type except normal motion.}
    \label{fig:motion_right_not_n}
  \end{figure}

@@

  % all techniques by patterns
  \begin{figure}
    \includegraphics[scale=0.65]{data/gnuplot/eps/patterns_all}
    \caption{All techniques by patterns.}
    \label{fig:patterns_all}
  \end{figure}

  % all techniques by black belt patterns
  \begin{figure}
    \includegraphics[scale=0.65]{data/gnuplot/eps/patterns_black_all}
    \caption{All techniques by black belt patterns.}
    \label{fig:patterns_black_all}
  \end{figure}

  % all techniques by color belt patterns
  \begin{figure}
    \includegraphics[scale=0.65]{data/gnuplot/eps/patterns_color_all}
    \caption{All techniques by color belt patterns.}
    \label{fig:patterns_color_all}
  \end{figure}

@@

  % left techniques by patterns
  \begin{figure}
    \includegraphics[scale=0.65]{data/gnuplot/eps/patterns_left}
    \caption{Left techniques by patterns.}
    \label{fig:patterns_left}
  \end{figure}

  % right techniques by patterns
  \begin{figure}
    \includegraphics[scale=0.65]{data/gnuplot/eps/patterns_right}
    \caption{Right techniques by patterns.}
    \label{fig:patterns_right}
  \end{figure}
